\section{This course}
This is the Spring \courseyear \course course studied by \nensei-year undergraduate international students at Kyushu University.

\subsection{What you need to do}
\begin{itemize}
    \item Borrow the book ``Engineering Mechanics: Dynamics'', 6th edition, by Meriam and Kraige from the Mechanical Engineering office on the 4th floor of West 4. The course will be based on that book and you will need to refer to it in class.
    \item Prepare a challenge-log in the form of a workbook or folder where you can clearly write the calculations you perform to solve each challenge. This will be used in the final assessment and will be occasionally reviewed by the teacher.
    \item Submit a weekly feedback form by \textbf{9am on Monday} before class at \url{https://goo.gl/forms/ULjtgmL0Q2fZbG292}.
    \item Please bring a wifi-capable internet device to class, as well as headphones if you need to access online components of the course during class. If you let me know in advance, I can lend computers and provide power extension cables for those who require them (limited number).
\end{itemize}

\subsection{How this works}
\begin{itemize}
    \item This booklet forms part of an active-learning segment in the course. The learning is self-directed in contrast to the traditional lecture-style model.
    \item Learning is guided through solving a series of challenges combined with instant feedback about the correctness of your answer.
    \item There are no lectures. Instead, there is discussion time. Here, you are encouraged to discuss any issues with your peers, teacher and any teaching assistants. Furthermore, you are encouraged to help your peers who are having trouble understanding something that you have understood; by doing so you actually increase your own understanding too.
    \item Discussion-time is from \disctime on \discdays at room \discroom.
    \item Peer discussion is encouraged, however, if you have help to solve a challenge, always make sure you do understand the details yourself. You will need to be able to do this in an exam environment. The questions on the exam will be similar in nature to the challenges.
    \item Every challenge in the book typically contains a \textbf{Challenge} with suggested \textbf{Resources} which you are recommended to utilise in order to solve the challenge. Occasionally the teacher will provide extra \textbf{Comments} to help guide your thinking. A \textbf{Solution} is also made available for you to check your answer. Sometimes this solution will be given in encrypted form. For more information about encryption, see section \ref{sec:hashes}.
    \item For deep understanding, it is recommended to study the suggested resources beyond the minimum required to complete the challenge.
    \item The challenge document has many pages and is continuously being developed. Therefore it is advised to view the document on an electronic device rather than print it. The date on the front page denotes the version of the document. You will be notified by email when the document is updated. The content may differ from last-year's document.
    \item A target challenge will be set each week. This will set the pace of the course and defines the examinable material. It's ok if you can't quite reach the target challenge for a given week, but you should be careful not to fall behind, since the exam cannot be delayed.
    \item You may work ahead, even beyond the target challenge, if you so wish. This can build greater flexibility into your personal schedule, especially as you become busier towards the end of the semester.
    \item Your contributions to the course are strongly welcomed. If you come across resources that you found useful that were not listed by the teacher or points of friction that made solving a challenge difficult, please let the teacher know about it!
\end{itemize}

\subsection{Assessment}
In order to prove to outside parties that you have learned something from the course, we must perform summative assessments. You will receive a weighted score based on:

\begin{itemize}
    \item Challenge-log (10\%) - final state at the end of the course, showing your calculations for all the challenges in the course.
    \item Coursework (20\%)
    \item Mid-term exam (30\%)
    \item Final exam (40\%)
\end{itemize}

Final score = MAX(Weighted score, Final exam score)

\subsection{Course feedback}
Course feedback (unofficial): \url{https://goo.gl/forms/YycJxFH0uuoBYCru1}
